Clustering in a hyperbolic model of complex networks.

### 2019-05-28 proofs_finite_k.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

\subsubsection{Truncation}
Consider the truncated Poissonized KPKVB model $\GPoH$ with $H =H_n= \frac{R}{4}$.
%H,R-H tend to infinity and coupling is still exact
\begin{lemma}\label{lem:n1}
Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. Then $\E N_1(H) = o(n)$.%If $H \rightarrow \infty$, 
%For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
\end{lemma}
\begin{proof}
By the Poisson distribution of the number of points inside the disk with radius $R-H$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
\begin{align*}
\E N_1(H) = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
\end{align*}
\end{proof}
\begin{lemma}\label{lem:n2}
Let $N_2(H)$ denote the number of vertices with at least one neighbour with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model. If $H \rightarrow \infty$, then $\E N_2(H) = o(n)$.
\end{lemma}
\begin{proof}
Among the vertices with at least one neighbour with radial coordinate at most $R-H$, we distinguish between those that themselves have radial coordinate at most $R-H_0$ and those that themselves have radial coordinate at least $R-H_0$ where $H_0 = \log H$. We will show that the expectation of both numbers is sublinear in $n$.

Since $H \rightarrow \infty$ we also have that $H_0 = \log H \rightarrow \infty$. Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\E N_1(H_0) = o(n)$ is sublinear. For a vertex with radial coordinate at least $R-H_0$, the probability that it has a neighbour with radial coordinate at most $R-H$, tends to zero. Therefore, by the Campbell-Mecke formula the number of such vertices is sublinear.
\end{proof}

@@

By Lemma~\ref{lem:n1}, we have that $\E X_1 = \E X_3 = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\E X_2 = o(n)$. We conclude that $\E |c(k;\GPo)-c(k;\GPoH)| = o(1)$. From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$, $\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1)$.
\end{proof}
\subsubsection{Coupling}
\begin{lemma}\label{lem:coup}
The clustering function in the truncated Poissonized KPKVB model $\GPoH$ and in the truncated box model $\GboxH$ agree, i.e. $c(k;\GPoH) = c(k;\GboxH)$.
\end{lemma}
\begin{proof}
As all vertices involved have height $\leq H$ resp. radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, therefore by Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box. So the two graphs are isomorphic and hence the clustering functions agree.
\end{proof}

@@

By the Campbell-Mecke formula, we have
\begin{align*}
\E X = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
\end{align*}
Then, we condition on the additional vertex $(0,y) \in \Rcal_H$ having degree $k$,
\begin{align*}
\E X = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
\end{align*}
We observe that for $H \rightarrow \infty$, the integrand converges point-wise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
\begin{align*}
\E X \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
$$Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)$$ and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$. As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
\begin{align*}
\E Y_1 = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2).
\end{align*}
If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $|x_1-x_2|>2e^H$, their neighbourhood balls are disjoint w.r.t. the connection rule of the truncated box model $\GboxH$. To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$. Then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$. As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.

Due to the disjointedness of the neighbourhood balls and the properties of the Poisson process $h(V,v_1)$ and $h(V,v_2)$ are independent. The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$. Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{4\nu e^H}{\pi n} = o(1)$. Writing $d_H$ for the horizontal distance, we can continue the calculation of the second moment,
\begin{align*}
\E Y_1 &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
&\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
&= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
&= (1+o(1)) (n\E X)^2.
\end{align*}
It follows that $\E X^2 = (1+o(1))(\E X)^2$, which implies $Var(X) \rightarrow 0$ using that $\E X$ tends to a constant (see above). We conclude
$$X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.$$
In a similar way, by the Campbell-Mecke formula,
\begin{align*}
\E Z =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
\end{align*}
By the theorem of dominated convergence, it follows that
\begin{align*}
\E Z \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
The statement that $Var(Z) \rightarrow 0$ follows by the same steps as for $X$, just using $h(V,v) = \1_{\{D_{\GboxH}(v)=k\}}$ instead. Hence,
\begin{align*}
\E Z \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
Finally note that 
\begin{align*}
\gamma(k) = \frac{\int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy}{\int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy}.
\end{align*}

@@

\begin{proofof}{Theorem~\ref{thm:maincc}}
Let $\epsilon >2\delta >0$.
As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
From Equations~\eqref{eq:def_pk}, \eqref{eq:gammakint} and \eqref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$. Write $p(k;G_n)=\frac{N_n(k)}{n}$ for the fraction of degree $k$ vertices in the KPKVB model. From the definition of the clustering coefficient and function, it follows immediately that $c(G_n) = \sum_{k=2}^\infty c(k;G_n)p(k;G_n)$. By the initial observation, it follows again that $(1-\delta)c(k;G_n) < \sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \leq 1$, and hence, $|c(G_n)-\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n)| \leq \delta$.
Putting these observations together:
\begin{align*}
|c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
 &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta. 
\end{align*}
Therefore, $\Pee(|c(G_n)-\gamma|\geq \epsilon) \leq \Prob{\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta} \rightarrow 0$ because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that $\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k$. %p_k =  = \Theta(k^{-(2\alpha +1)})
\end{proofof}

>>>>

\subsubsection{Truncation}
Consider the truncated Poissonized KPKVB model $\GPoH$ with $H =H_n= \frac{R}{4}$.
%H,R-H tend to infinity and coupling is still exact
\begin{lemma}\label{lem:n1}
Let $N_1(H)$ denote the number of vertices with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model $\GPo$. Then $\Exp{N_1(H)} = o(n)$.%If $H \rightarrow \infty$, 
%For all $\epsilon >0$, there is $H_\epsilon$ such that for all $H\geq H_\epsilon$, it holds that $\E N_1(H) \leq \epsilon n$.
\end{lemma}
\begin{proof}
By the Poisson distribution of the number of points inside the disk with radius $R-H$, by the asymptotic behaviour of $\cosh$ and using that all $R, R-H, H \rightarrow \infty$,
\begin{align*}
\Exp{N_1(H)} = n \frac{\cosh(\alpha(R-H))-1}{\cosh(\alpha R) -1} = (1+o(1)) n e^{-\alpha H} = o(n)
\end{align*}
\end{proof}
\begin{lemma}\label{lem:n2}
Let $N_2(H)$ denote the number of vertices with at least one neighbour with radial coordinate at most $R-H \in [0,R]$ in the Poissonized KPKVB model. If $H \rightarrow \infty$, then $\Exp{N_2(H)} = o(n)$.
\end{lemma}
\begin{proof}
Among the vertices with at least one neighbour with radial coordinate at most $R-H$, we distinguish between those that themselves have radial coordinate at most $R-H_0$ and those that themselves have radial coordinate at least $R-H_0$ where $H_0 = \log H$. We will show that the expectation of both numbers is sublinear in $n$.

Since $H \rightarrow \infty$ we also have that $H_0 = \log H \rightarrow \infty$. Hence by Lemma~\ref{lem:n1}, the expected number of vertices with radial coordinate at most $R-H_0$ (in particular those vertices among them with at least one neighbour with radial coordinate at most $R-H$), $\Exp{ N_1(H_0) = o(n)}$ is sublinear. For a vertex with radial coordinate at least $R-H_0$, the probability that it has a neighbour with radial coordinate at most $R-H$, tends to zero. Therefore, by the Campbell-Mecke formula the number of such vertices is sublinear.
\end{proof}

@@

By Lemma~\ref{lem:n1}, we have that $\Exp{ X_1} = \Exp{ X_3} = o(n)$ and by Lemma~\ref{lem:n2}, we have that $\Exp{ X_2} = o(n)$. We conclude that $\E |c(k;\GPo)-c(k;\GPoH)| = o(1)$. From this, convergence in probability follows by Markov's inequality: for $\epsilon >0$, 
\[
	\Pee(|c(k;\GPo)-c(k;\GPoH)| \geq \epsilon) \leq \frac{\E|c(k;\GPo)-c(k;\GPoH)|}{\epsilon} = o(1).
\]
\end{proof}
\subsubsection{Coupling}
\begin{lemma}\label{lem:coup}
The clustering function in the truncated Poissonized KPKVB model $\GPoH$ and in the truncated box model $\GboxH$ agree, i.e. $c(k;\GPoH) = c(k;\GboxH)$.
\end{lemma}
\begin{proof}
As all vertices involved have height $\leq H$ resp. radial coordinate $\geq R-H$ and as $H\leq \frac{R}{4}$, all vertices involved (in the disk)  will have radial coordinate $\geq \frac{3}{4}R$, therefore by Lemma~\ref{lem:coupling_edges}, edges exist between such vertices in the disk if and only if they exist in the box. So the two graphs are isomorphic and hence the clustering functions agree.
\end{proof}

@@

By the Campbell-Mecke formula, we have
\begin{align*}
\Exp{ X} = \frac{1}{n}\int_{\Rcal_H} \E h(V,v) \mu(dv) = \int_0^H \E h(V,(0,y))\alpha e^{-\alpha y} dy.
\end{align*}
Then, we condition on the additional vertex $(0,y) \in \Rcal_H$ having degree $k$,
\begin{align*}
\Exp{ X} = \int_0^H \E[h(V,(0,y))|D_{G_{box,H}}(0,y)=k]\Pee(D_{G_{box,H}}(0,y)=k)\alpha e^{-\alpha y}dy.
\end{align*}
We observe that for $H \rightarrow \infty$, the integrand converges point-wise for $y \in (0,\infty)$ to $P(y)\rho(y,k)\alpha e^{-\alpha y}$ and is always bounded by the integrable function $\alpha e^{-\alpha y}$.
Therefore, by the theorem of dominated convergence, as $H \rightarrow \infty$,
\begin{align*}
\Exp{X} \rightarrow \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
Note that for $X^2$, the summation can be split into off-diagonal (with $v_1 \not = v_2$) and diagonal (with $v_1=v_2$) terms, i.e. write $X^2 = \frac{1}{n^2}(Y_1+Y_2)$ where 
\[
	Y_1 = \sum_{v_1 \not = v_2 \in V(G_{box,H})} h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2),
\] 
and $Y_2 = \sum_{v_1 \in V(G_{box,H})} h(V(G_{box,H}),v_1)^2$. As $h \leq 1$, $Y_2 \leq n X\leq n$ and so, $\E Y_2 \leq n$, we have by the Campbell-Mecke formula,
\begin{align*}
\Exp{Y_1} = \int_{\Rcal_H} \int_{\Rcal_H} \E[h(V(G_{box,H}),v_1)h(V(G_{box,H}),v_2)]\mu(dv_1)\mu(dv_2).
\end{align*}
If $v_1=(x_1,y_1)$ and $v_2=(x_2,y_2)$ have horizontal distance $|x_1-x_2|>2e^H$, their neighbourhood balls are disjoint w.r.t. the connection rule of the truncated box model $\GboxH$. To see this, assume that $v_3=(x_3,y_3)$ is adjacent to both $v_1$ and $v_2$. Then $|x_1-x_3|\leq e^{\frac{1}{2}(y_1+y_3)}$ and $|x_2-x_3|\leq e^{\frac{1}{2}(y_2+y_3)}$. As $y_1, y_2, y_3 \leq H$, it follows that $|x_1-x_3| \leq e^H$ and $|x_2-x_3|\leq e^H$, which implies that $|x_1-x_2| \leq |x_1-x_3|+|x_2-x_3|\leq 2e^H$, contradiction.

Due to the disjointedness of the neighbourhood balls and the properties of the Poisson process $h(V,v_1)$ and $h(V,v_2)$ are independent. The horizontal distance is uniform in $[0,\frac{\pi n}{2\nu}]$. Therefore, the probability that two vertices have horizontal distance $\leq 2e^H$ is $\leq \frac{4\nu e^H}{\pi n} = o(1)$. Writing $d_H$ for the horizontal distance, we can continue the calculation of the second moment,
\begin{align*}
\Exp{ Y_1} &= \int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|>2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2)\\
&\qquad+\int_{} \int_{\substack{\Rcal_H\times \Rcal_H:\\ |x_1-x_2|\leq2 e^H}} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
&= (1+o(1))\int_{} \int_{\Rcal_H\times \Rcal_H} \E[ h(V,v_1)]\E[h(V,v_2)]\mu(dv_1)\mu(dv_2) \\
&= (1+o(1)) (n\E X)^2.
\end{align*}
It follows that $\Exp{ X^2} = (1+o(1))\Exp{ X}^2$, which implies $Var(X) \rightarrow 0$ using that $\Exp{ X}$ tends to a constant (see above). We conclude
\[
	X \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy.
\]
In a similar way, by the Campbell-Mecke formula,
\begin{align*}
\Exp{Z} =\frac{1}{n} \int_{\Rcal_H} \Pee(D_{G_{box,H}}(v)=k) \mu(dv) = \int_0^H \Pee(D_{G_{box,H}}(0,y)=k) \alpha e^{-\alpha y}dy.
\end{align*}
By the theorem of dominated convergence, it follows that
\begin{align*}
\Exp{ Z} \rightarrow \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
The statement that $Var(Z) \rightarrow 0$ follows by the same steps as for $X$, just using $h(V,v) = \1_{\{D_{\GboxH}(v)=k\}}$ instead. Hence,
\begin{align*}
\Exp{ Z} \xrightarrow[n\rightarrow\infty]{\Pee} \int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy.
\end{align*}
Finally note that 
\begin{align*}
\gamma(k) = \frac{\int_0^\infty P(y)\rho(y,k)\alpha e^{-\alpha y}dy}{\int_0^\infty \rho(y,k)\alpha e^{-\alpha y}dy}.
\end{align*}

@@

\begin{proofof}{Theorem~\ref{thm:maincc}}
Let $\epsilon >2\delta >0$.
As the $p_k$ form the probability mass function of an $\N_0$-valued random variable, we have that $\sum_{k=0}^\infty p_k = 1$, which implies that there is $K_\delta >0$ such that $1-\delta < \sum_{k=0}^{K_\delta} p_k \leq 1$.
From Equations~\eqref{eq:def_pk}, \eqref{eq:gammakint} and \eqref{eq:gammaint}, we know that $\gamma = \sum_{k=2}^\infty \gamma(k)p_k$. 
From this, it follows that $(1-\delta)\gamma < \sum_{k=2}^{K_\delta} \gamma(k) p_k \leq 1$ and hence that $|\gamma - \sum_{k=2}^{K_\delta} \gamma(k)p_k| \leq \delta$. Write $p(k;G_n)=\frac{N_n(k)}{n}$ for the fraction of degree $k$ vertices in the KPKVB model. From the definition of the clustering coefficient and function, it follows immediately that $c(G_n) = \sum_{k=2}^\infty c(k;G_n)p(k;G_n)$. By the initial observation, it follows again that $(1-\delta)c(k;G_n) < \sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \leq 1$, and hence, $|c(G_n)-\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n)| \leq \delta$.
Putting these observations together:
\begin{align*}
|c(G_n)-\gamma| &\leq \left|c(G_n)-\sum_{k=2}^{K_\delta}c(k;G_n)p(k;G_n)\right|+\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\left|\sum_{k=2}^{K_\delta} \gamma(k)p_k-\gamma\right| \\
 &\leq \delta +\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| +\delta. 
\end{align*}
Therefore, 
\[
	\Prob{|c(G_n)-\gamma|\geq \epsilon} \leq \Prob{\left|\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) -\sum_{k=2}^{K_\delta} \gamma(k)p_k\right| \geq \epsilon - 2\delta} \rightarrow 0,
\] 
because $c(k;G_n) \xrightarrow{\Pee} \gamma(k)$ for $k=2,\dots,K_\delta$ and $p(k;G_n) \xrightarrow{\Pee} p_k$ together imply that 
\[
	\sum_{k=2}^{K_\delta} c(k;G_n)p(k;G_n) \xrightarrow{\Pee} \sum_{k=2}^{K_\delta} \gamma(k) p_k.
\]
\end{proofof}

### 2019-05-28 proofs_infinite_k.tex
included all comments from Nikolaos and made final changes. Ready for Tobias.

\begin{remark}[Diverging $k_n$]
Throughout the remainder of this paper, unless stated otherwise, $\{k_n\}_{n \ge 1}$ will always denote a sequence of integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
\end{remark}

>>>>

\begin{remark}[Diverging $k_n$]
Throughout the remainder of this paper, unless stated otherwise, $\{k_n\}_{n \ge 1}$ will always denote a sequence of non-negative integers satisfying $k_n \to \infty$ and $k_n = \smallO{n^{\frac{1}{2\alpha + 1}}}$, as $n \to \infty$.
\end{remark}
